%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,roman]{moderncv}

\usepackage[T1]{fontenc}
\usepackage{multicol}

\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[scale=0.87]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{3cm} % Change the width of the dates column
\setlength{\makecvtitlenamewidth}{6cm}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Arnaud}
\familyname{Beaussier}

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{ADDRESS}{CITY, STATE}
\mobile{PHONENUMBER}
\email{MAILADRESS}
\homepage{https://www.linkedin.com/in/beaussierarnaud}{linkedin/beaussierarnaud}
\quote{Site Reliability Engineer \& Developer}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE 
%----------------------------------------------------------------------------------------

\section{Experience}

\subsection{Site Reliability Engineer \& Developer}

\cventry{Aug 2017--Present}{1 yrs 3 mos}{\textsc{Claranet}}{Paris}{Employee}{I joined the developers team in charge of internal tools related to hosted service provider applications (CMDB, Secrets management, resources usage reporting, etc.), and supports functions like HR and financial Service. I work on web programming tasks with \textbf{Scrum}, mainly with \textbf{Symfony PHP} framework and \textbf{Python}. Precisely,I contributed to the creation of \textbf{code-guidelines}and to add functionality to existing applications.I build from scratch one related to managing and transmitting secrets. My profile, which is very \textbf{SRE oriented}, brings to the team a know-how in terms of improvement of the \textbf{service availability}, and of the deployment processes while integrating the \textbf{DevOps} philosophy of work which was previously lacked. Besides,I provide infrastructure related formations to my team in order to bring a deeper comprehension on the problems a hosted service provider could have, as well as technical rules affected by business rules of the domain. Claranet, being an \textbf{ISO / IEC 27001} certified company, I work closely with our CISO, Q\&A managers and external auditors to continuously \textbf{improve the security} of our information service, through code audit or external penetration tests.
\begin{multicols}{3}
	\begin{itemize}
		\item {Docker}
		\item {Kubernetes}
		\item {VmWare}
		\item {PHP 7}
		\item {GraphQL}
		\item {Python 3}
	\end{itemize}
\end{multicols}}

%------------------------------------------------
\begin{center}
\line(1,0){250}
\end{center}
\subsection{Site Reliability Engineer}

\cventry{May 2015--Aug 2017}{2 yrs 3 mos}{\textsc{Oxalide}}{Paris}{Employee}{I joined Oxalide within the specialized team for \textbf{Media and Press} as a \textbf{SRE},implying a \textbf{technical escalation} L2 and L3 and a regular \textbf{night-time on-call}. My projects involved a resumption of existing infrastructure managed by customers. Beginning with a \textbf{technical audit}, followed by a phase of improvement \textbf{advices}, finished with a \textbf{complete overhaul} involving a migration on \textbf{AWS}. A \textbf{training phase} could be helpful if necessary. As result, I've developped strong knowledges on\textbf{Debian}, \textbf{Chef}, \textbf{Terraform} and \textbf{AWS} on a daily basis, as well as various middlewares in fonction of the customer. I'm keen on analyzing\textbf{in-depth cases}related to recurring incidents, discussing about\textbf{infrastructure costs}, or unsatisfaying\textbf{performances}. I offered regularly \textbf{formations on Web-Performance} on Nginx and Varnish, about \textbf{deployment workflow} with Capistrano to newcomers. Last but not least, I was in charge of \textbf{technical entrance tests} and interviews for the recruitment.
\begin{multicols}{3}
	\begin{itemize}
		\item {AWS}
		\item {Terraform}
		\item {Chef}
		\item {Debian}
		\item {Golang}
	\end{itemize}
\end{multicols}}

%------------------------------------------------
\begin{center}
\line(1,0){250}
\end{center}
\subsection{GNU / Linux System and Network Administrator}

\cventry{Apr 2013--Jun 2013}{3 mos}{\textsc{Sutunam}}{Vietnam Hanoi}{Intern}{I joined a startup specialized in \textbf{Magento and Symfony} frameworks in Hanoi. I managed their virtualization servers running on \textbf{Debian XEN}, and I operate on the complete overhaul of the office internal networks. I implemented a logical isolation between "business" networks and the "guest" one by the use of \textbf{VLAN} with \textbf{QOS} rules with \textbf{Iptables} to conserve bandwidth for critical services.
\begin{multicols}{3}
	\begin{itemize}
		\item {XEN}
		\item {Debian}
		\item {NetGear}
	\end{itemize}
\end{multicols}}

%------------------------------------------------
% Associate
%------------------------------------------------
\subsection{Cofounder \& Site Reliability Engineer \& Developer}

\cventry{Nov 2013--Present}{5 yrs}{\textsc{Remote}}{}{Associate}{I founded an \textbf{independent gaming studio} named Electric-Dragons with 6 associates in France. This studio published a variation of the \textbf{chess game} called Deep-Chess which uses the \textbf{recursion principle} and we are actually developing a \textbf{strategy games}. We also do \textbf{web development} projects for local communities and associations. Our code base is mainly in \textbf{Rust language} and our websites are built with the \textbf{Django Python} framework. I manage the company, \textbf{accounting}, \textbf{declaration of result}, edition of the balance sheets and the obligatory legal documents. I also manage our servers (hosted on the \textbf{OVH Cloud}) and contibute on my free-time on our applications, addition of functionality, bugfixes, testing and improvement of the \textbf{CI/CD}.
\begin{multicols}{3}
	\begin{itemize}
		\item {Django Python}
		\item {PostgreSQL}
		\item {Rust}
	\end{itemize}
\end{multicols}}

%------------------------------------------------
% Freelance
%------------------------------------------------
\begin{center}
\line(1,0){250}
\end{center}
\subsection{SEO consultant}

\cventry{2018}{Occasionally}{\textsc{Remote}}{}{Freelance}{I also carry out several \textbf{SEO audits} for a French real estate company. These audits focus on improvements of the \textbf{SEO strategy} for natural referencing. It includes analysis of their sites \textbf{performance}, quality of the backlinks, editorial quality of the articles, choice of HTML anchors, and application of the best SEO practices to \textbf{generate user activity}.}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2014}{Bachelor in computer science}{National Conservatory of Arts and Crafts}{Paris}{}{}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}

\cvitem{Basic}{\textsc{Rust}}
\cvitem{Intermediate}{\textsc{Python},\textsc{Golang},\textsc{PHP},\textsc{AWS},\textsc{Nginx},\textsc{Varnish},\LaTeX}
\cvitem{Advanced}{Site Reliability Engineering, Gnu/Linux administration, GitLab-CI, DevOps methodology}

%----------------------------------------------------------------------------------------
%	MANAGEMENT AND SOFT SKILLS
%----------------------------------------------------------------------------------------

\section{Management and software development Methods}

\cvitem{Management}{Lean, Visual management}
\cvitem{Agile}{Scrum}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{French}{Mothertongue}{}
\cvitemwithcomment{English}{Intermediate}{Conversationally fluent}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\renewcommand{\listitemsymbol}{-~}

\cvlistitem{Open Source Software enthousiats - Member of April, a French advocacy association devoted to promoting and protecting Free/Libre Softwa:re}
\cvlistitem{Child protection and inclusion - UNICEF donator}
\cvlistitem{Classical Guitar - 5 years}

%----------------------------------------------------------------------------------------

\end{document}
